---
title: "Machine Learning 1 - Assignment"
author: "Annalena Kreischer, Ansam Zedan & Mélanie Bigler"
date: "HS23"
output: 
  html_document:
    toc: yes
    toc_depth: 2
    toc_float:
    number_sections: yes
    code_folding: hide
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include = FALSE, warning = FALSE}
library(knitr)
opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  warning = FALSE,
  message = FALSE)

```

\newpage

# Management Summary

add in the end

# Introduction (Annalena)

## Motivation (Annalena)

what is the motivation

## Goal

what is the outcome?

## Data source

The data was used from this source:

<https://www.kaggle.com/datasets/pavansubhasht/ibm-hr-analytics-attrition-dataset>

# Data Preperation

## Libraries

```{r libraries}
#all used lirbaries for this report
library(readr)

```

## Loading data

```{r loading_data}

#set workin diretory to current file
# setwd("../projectML")

#loading total dataset
d.full.attrition <- read.csv("../projectML/data/WA_Fn-UseC_-HR-Employee-Attrition.csv", 
                             header = TRUE)
str(d.full.attrition)


#define set for training
# d.train.attrition <- d.full.attrition

  
#define set for testing
# d.test.attrition <- d.full.attrition
  
```

## Define factors

Which variables need to be set as factors?

```{r setting_factors}

```

# Graphical Analysis

What is data showing? Make some first easy visualizations

# Linear Model

# Generalised Linear Model with family set to Poisson

# Generalised Linear Model with family set to Binomial

# Generalised Additive Model

# Neural Network

# Support Vector Machine

# Solution to an optimisation problem

# Comparing Models

# Conclusion

## Learnings & Outlook
